\documentclass[10pt]{letter}
\usepackage{UPS_letterhead,color}
\newcommand{\alert}[1]{\textcolor{red}{#1}}

\begin{document}

\begin{letter}%
{To the Editors of the Journal of Chemical Physics}

\opening{Dear Editors,}

Please find attached a manuscript entitled
``Spin adaptation with determinant-based selected configuration interaction'', which
we would like to submit as a Regular Article in the \textit{Journal of Chemical Physics}.

In the context of selected configuration interaction (sCI), obtaining spin
adapted wave functions can be enforced by working with configuration state
functions.  If one wants to stay in the determinant-based formalism, obtaining
spin adapted wave functions can be enforced by adding to the internal space all
missing determinants with the same space part as the selected determinants.  We
introduce in this paper an original algorithm for the generation of these
determinants.  The presented algorithm generates the determinants so fast that
this step is completely negligible compared to the rest of the sCI calculation.

In addition, we propose a modification of the denominators in the Epstein-Nesbet
perturbation theory which reduces significantly the lack of invariance 
with respect to the spin quantum number of the wave function. This modification
does not change the computational cost of the perturbative energy correction.

In view of the considerable interest of selected configuration interaction 
methods, we believe that the Journal of Chemical Physics is
the most appropriate journal to publish the present algorithm.

\closing{Sincerely, the authors.}
\end{letter}
\end{document}
